The Tail Risk Premium - Extension of Lottery Preference Premium

### 2025-03-31 Animated Graph.qmd
Updated HTML
Updated Background

![](images/clipboard-1227717430.png)

---
title: ""
author: "Brayden Boyko"
format: html
editor: visual
---

>>>>

---
title: ""
author: ""
format: 
  html:
    embed-resources: true
    page-layout: full
    toc: false
    grid: 
      margin-width: 10px
      body-width: 1000px
    resources: 
      - "*.js"
      - "*.mp3"
editor: source
---
<style>
body {
  background-color: #1D1D1B;
}
</style>
